\documentclass{resume}

\setlength{\footheight}{49.59999pt}

\rohead{\thepage\ of \pageref{LastPage}}

\cofoot{
  \begin{spacing}{1.25}
    \small{
      \footerlocation{New York, NY} \
      % \footerphone{(555) 555-5555} \
      % \footerlink{http://dcousineau.com/} \
      \footeremail{dcousineau@gmail.com}
    } \\
    \small{\emph{
        \LaTeX source for this resum$\acute{e}$ located at \href{https://github.com/dcousineau/resume}{github.com/dcousineau/resume}
    }}
  \end{spacing}
}

\begin{document}

\name{Daniel Cousineau}
\smallskip

\section{Selected Experience}

\employer
{Ember Hiring}
{https://www.emberhiring.com}
{March 2023 --- \emph{Present}}
{Co-founder \& Head of Engineering}
{
  \begin{jobitems}
  \item Co-founded travel-nurse staffing startup centered on AI-powered job matching; owned technical strategy and execution. Built and led a 3-engineer team (5-person company) using AI dev tooling for speed to market; bootstrapped to \textasciitilde\$20K MRR.
  \item Built greenfield customer products and internal platform from scratch, including:
    \begin{jobitems}
    \item Real-time match notifications via Web Push, Slack, Microsoft Teams, and Email.
    \item OAuth-secured MCP server letting customers connect their own AI models.
    \item AWS multi-account (CloudFormation + CDK); containerized Node.js (Next.js, Fastify) \& Python data services on Fargate.
    \end{jobitems}
  \item Wore every founder hat --- Sales, Customer Success, and Product roadmap driven by direct customer interviews and tight iteration.
\end{jobitems}}

\employer
{GoDaddy}
{https://www.godaddy.com}
{August 2020 --- March 2024}
{Director of Engineering, UXPlatforms \& Open Source }
{
  \begin{jobitems}
  \item Led the UXPlatform organization (\textasciitilde15 engineers across the UXCore and Experience Infrastructure teams) as a manager of managers --- 2 engineering managers and 1 principal engineer reporting directly; fully owned hiring, compensation, and performance management for platforms serving 1000+ engineers across all Business Units and brands.
    \begin{jobitems}
    \item UXCore delivered the multi-brand design system component library --- 230 themes across \textasciitilde18 brands --- adopted by \textasciitilde100\% of actively maintained applications across all 5 business pillars.
    \item Experience Infrastructure (XI) delivered shared navigation UI, internal APIs, and globally distributed CDN assets (Americas, Europe, Asia) to every customer-facing and logged-in property at a 99.99\% uptime SLA.
    \item Both teams published documentation, ran trainings, and held quarterly roadmap planning with downstream consuming teams.
    \end{jobitems}
  \item Drove \textasciitilde100\% version-upgrade compliance across consuming teams via codemod tooling, adoption dashboards, deprecation policy, and hands-on training --- cutting upgrade effort from days to hours and moving teams from chronically lagging to current with zero exceptions, lifting platform satisfaction on annual NPS-style surveys.
  \item Delivered company-wide regulatory compliance as inherited platform capabilities --- reached 100\% WCAG 2.0 AA (ADA) accessibility by baking it into UXCore, and shipped a geo-aware cookie-consent system (CPRA/CCPA, GDPR) through XI.
  \item Sponsored and ran the Open Source Working Group (GoDaddy's OSPO) --- managing a \textasciitilde\$100K annual sponsorship budget and company-wide OSS and inner-source policy; integrated the WordPress organization into the broader program.
  \item Partnered with senior leadership on multi-year platform roadmaps and stakeholder alignment across consuming teams.
\end{jobitems}}

\employer
{Rent the Runway}
{https://www.renttherunway.com}
{July 2019 --- July 2020}
{Staff Software Engineer}
{
  \begin{jobitems}
  \item Manage and run the Consumer Platform team, a tiger-team consisting of senior+ engineers responsible for cross cutting engineering projects and supporting other Consumer Engineering teams.
  \item Lead consumer frontend engineering efforts and standards, focused on improving process and discipline while upgrading legacy systems to modern practices.
  \item Helped focus career-ladder to be more inclusive of Frontend Engineering, evaluate \& level new Frontend Engineer candidates for fitness.
\end{jobitems}}

\employer
{Aalto}
{https://aalto.com}
{January 2018 --- June 2019}
{Founding Engineer}
{
  \begin{jobitems}
  \item Helped found and lead sustainable \& performant Frontend engineering practices from blank canvas through a Sequoia-led Seed raise.
  \item Helped architect and deploy a GKE based ``microlith'' service architecture
\end{jobitems}}

% \employer
%     {The Muse}
%     {https://themuse.com}
%     {February 2018 --- April 2018}
%     {Consulting Director of Engineering}
%     {Identified and established engineering organization and process improvements for multiple teams, but with a special focus on performance and growth.}

% \employer
%     {BounceX \emph{\ldots now Wunderkind}}
%     {https://www.wunderkind.co}
%     {October 2017 --- December 2017}
%     {Director of Engineering, Applications}
%     {Got hands-on early and led an emergency team to repair and scale a legacy system, from constant crashing to comfortably handling double prior traffic during Black Friday / Cyber Monday (readily hitting at 12,000 HTTP requests per second to database and redis backed services).}

\employer
{Grovo \emph{\ldots acquired by Cornerstone OnDemand}}
{}
{February 2016 --- August 2017}
{Director of Engineering, Frontend}
{
  \begin{jobitems}
  \item Directly managed all Frontend engineers in addition to leading all 3 cross-discipline product-facing pods spanning Backend and Data engineering disciplines.
  \item Promoted two senior engineers into their first Engineering Manager roles, becoming a manager of managers while delegating increased architectural and organizational responsibility.
  \item Spearheaded adoption of more formal agile project management.
  \item Established bug triage process across entire Engineering organization in collaboration with the Customer Success teams to improve reporting and intake procedures.
\end{jobitems}}

\employer
{Croscon \emph{\ldots now PolicyFly}}
{https://croscon.com}
{May 2013 --- February 2016}
{Senior Engineer / Engineering Manager}
{
  \begin{jobitems}
  \item Hired \& grew team from 3 to 11 engineers as a boutique engineering consultancy.
  \item Ensured high performance and on-time delivery for highly visible marketing projects for Google Zoo including interactive video builder for the Lays ``Do Us A Flavor'' campaign.
  \item Architected and built SPA e-commerce applications for clients acting as their startup's first engineering team.
  \item Architected and built a high volume document management system in Python \& C++ using the Tesseract OCR tool to automate entry of financial reports.
\end{jobitems}}

% \employer
%     {Splash Media}
%     {}
%     {February 2012 --- May 2013}
%     {Software Wizard}
%     {}

% \employer
%     {RAPP}
%     {https://rapp.com}
%     {March 2011 --- January 2012}
%     {Interactive Software Engineer}
%     {}
%     % {Built an ADDY award winning interactive movie memory wall using Python \& Javascript for AMC Theatres for use in booths at public events such as their Comicon San Diego after-party and the 2011 Emmy Awards.}

% \employer
%     {Moverati}
%     {}
%     {September 2010 --- March 2011}
%     {Developer}
%     {}
%     % {Developed new product features \& ensured site scaled with spikes in traffic during events such as the NFL Superbowl Experience 2011.}

% \employer
%     {Texas A\&M Division of Student Affairs Department of IT}
%     {https://doit.tamu.edu}
%     {April 2009 --- September 2010}
%     {Senior Software Applications Developer}
%     {}
%     % {Developed Zend Framework, Doctrine 1.x, \& Python applications.}
\addstackgap[1em]{\emph{Full employment history dating back to 2006 available at \href{https://www.linkedin.com/in/dcousineau/}{https://www.linkedin.com/in/dcousineau}}}

\section{Notable Participation}

\employer
{OpenJS Foundation}
{https://openjsf.org}
{October 2021 --- March 2024}
{Member, Board of Directors}
{Elected by peers to represent Gold sponsors on the OpenJS Foundation Board of Directors on behalf of GoDaddy.}

%% \section{Selected Open Source Contributions}
%%
%% \project
%%     {Phorever}
%%     {https://github.com/dcousineau/phorever}
%%     {Creator}
%%     {PHP-based daemon \& long-running process manager.}
%% \\ \\ \\
%% \project
%%    {Spaz / SpazHD for HP WebOS}
%%    {http://getspaz.com/}
%%     {\small{(Former)} \normalsize{Contributor}}
%%     {A fully open-source twitter client for HP WebOS devices including the TouchPad.}

\section{Selected Presentations}

\begin{spacing}{1.35}
  \href{https://speakerdeck.com/dcousineau/time-is-a-social-construct}{``Time is a Social Construct''} --- \href{https://2019.jsconf.us/speakers/daniel-cousineau}{JSConf 2019}\\
  % \href{https://speakerdeck.com/dcousineau/react-at-scale}{``React @ Scale''} --- \href{https://www.longhornphp.com}{LonghornPHP 2019}\\
  % \href{https://speakerdeck.com/dcousineau/frontend-performance-and-you}{``Frontend Performance \& You''} --- \href{https://www.longhornphp.com}{LonghornPHP 2019}\\
  % \href{https://speakerdeck.com/dcousineau/feature-flags-and-you}{``Feature Flags \& You''} --- \href{http://brooklynjs.com}{BrooklynJS 2017}\\
  % \href{https://speakerdeck.com/dcousineau/react-plus-redux-at-scale}{``React+Redux @ Scale"} --- \href{https://qconnewyork.com/ny2017/presentation/reactredux-scale-talk}{QCon New York 2017}\\
  % \href{https://speakerdeck.com/dcousineau/how-not-writing-php-makes-you-better-at-php}{``How Not Writing PHP Makes You Better At PHP"} --- \href{https://conference.phpbenelux.eu/2015/}{PHPBenelux 2015}\\
  % \href{https://speakerdeck.com/dcousineau/reframing-the-problem-dcjs-july-2016}{``Reframing the Problem"} --- \href{http://2014.madisonphpconference.com/schedule/view/19/reframing-the-problem-daniel-cousineau}{MadisonPHP 2014} Keynote \& \href{http://truenorthphp.ca/}{True North PHP 2014}\\
  % \href{https://speakerdeck.com/dcousineau/queues-and-the-giant-beanstalkd}{``Queues and the Giant beanstalkd"} --- \href{http://confoo.ca/}{ConFoo 2013}\\
  \emph{Full presentation history can be found at \href{https://speakerdeck.com/dcousineau}{https://speakerdeck.com/dcousineau}}
\end{spacing}

\section{Education, Community \& Awards}

\stdtable{
  School              & Texas A\&M University \hfill Class of 2009\\
  Degree              & B.S., Computer Science; Minor, Business Administration\\
}
\\
\begin{spacing}{1.35}
  Co-Organizer \& Co-Founder of the QueensJS meetup \emph{(2014--2020)}
  \\
  Co-Organizer of the DallasPHP meetup \emph{(2011--2013)}
  \\
  Co-Organizer of the \href{http://empirejs.org/}{EmpireJS Conference} \emph{(2016--2018)}
  \\
  Co-Organizer of the \href{http://lonestarphp.com/}{Lone Star PHP Conferences} \emph{(2012--2017)}
  \\
  Eagle Scout Rank, Boy Scouts of America, 2004
\end{spacing}

\end{document}
